EGALITARIAN ASPECTS OF SCALE-FREE NETWORKS

### 2017-08-20 article/article.tex
detail

\subsection*{\textit{Acknowledgements}}
The authors thanks CNPq for the funding received while researching the topic of this article,
the researchers of IFSC/USP and ICMC/USP for the recurrent collaboration in every situation
where we needed directions for investigation.

>>>>

\subsection*{\textit{Acknowledgements}}
The authors thank CNPq for the funding received while researching the topic of this article,
the researchers of IFSC/USP and ICMC/USP for the recurrent collaboration in every situation
where we needed directions for investigation.
